Function to find association b/w n significant eigen genes of meta modules with Diagnosis, Diagnosis.Gender, ApoE

### 2017-10-16 code/Rmd/networkAssociationTest_metaModules.Rmd
Major modifications

    Heatmap(mdl.ovrlp, col = colorRamp2(seq(0,1,length.out = 5), viridis::viridis(5)),
            name = 'JacDist', cell_fun = function(j,i,x,y,wifht,height,fill){
              grid.text(mdl.ovrlp.log[i,j] %>% format(digits = 1), x, y)
            })
  }
```

### Associaiton with Diagnosis
```{r Dx, fig.height=5, fig.width=10}
# Find assocition b/w Diagnosis category with n eigen genes
FORMULA = as.formula('PC~Diagnosis+Batch+RIN+PCT_INTRONIC_BASES+PMI+PCT_INTERGENIC_BASES+AOD+PCT_PF_READS_ALIGNED+Gender')
assoc.stat.diagnosis = MODULES %>%
  dplyr::filter(GeneID %in% rownames(EXPR)) %>%
  plyr::dlply(.(ModuleName, brainRegion), .fun = findAssociationStatistics, 
              COVARIATES, EXPR, FORMULA,
              .parallel = T, .paropts = list(.packages = c('dplyr', 'data.table')))

@@

writeLines('Percent of modules whose PC1 is significantly associated')
Dx %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::summarise(nsig = round(sum(pc1.fdr <= 0.05)/sum(pc1.fdr <= 1) * 100, 2)) %>%
  kable()
```

### Associaiton with Diagnosis.Gender
```{r Dx.Gender, fig.height=5, fig.width=10}
# Find assocition b/w Diagnosis.Gender category with n eigen genes
COVARIATES$Diagnosis.Gender = paste(COVARIATES$Diagnosis, COVARIATES$Gender, sep= '.') %>%
  as.factor
FORMULA = as.formula('PC~Diagnosis.Gender+Batch+RIN+PCT_INTRONIC_BASES+PMI+PCT_INTERGENIC_BASES+AOD+PCT_PF_READS_ALIGNED')
assoc.stat.diagnosis.gender = MODULES %>%
  dplyr::filter(GeneID %in% rownames(EXPR)) %>%
  plyr::dlply(.(ModuleName, brainRegion), .fun = findAssociationStatistics, 
              COVARIATES, EXPR, FORMULA,
              .parallel = T, .paropts = list(.packages = c('dplyr', 'data.table')))

@@

p = ggplot(Dx.gender, aes(x = ngenes, y = total.eff.sz, color = brainRegion)) + geom_point()
p = p + xlab('No. of genes') + ylab('Total Effect Size')
p + theme(legend.position = 'top')

p = ggplot(Dx.gender, aes(x = as.factor(npc.sig), y = total.eff.sz, color = brainRegion)) + geom_boxplot()
p = p + xlab('No. of genes') + ylab('Total Effect Size')
p + theme(legend.position = 'top')

@@

p = ggplot(Dx.gender, aes(x = brainRegion, y = pc1.eff.sz, color = -log10(pc1.fdr))) + geom_boxplot() + geom_jitter()
p = p + coord_flip() + xlab('Brain Region') + ylab('PC1 Effect Size')
p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')

writeLines('Number of significantly associated modules')
Dx.gender %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::summarise(nsig = sum(total.fdr <= 0.05),
                   ntotal = sum(total.fdr <= 1)) %>%
  kable()

writeLines('Percent of significantly associated modules')
Dx.gender %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::summarise(nsig = round(sum(total.fdr <= 0.05)/sum(total.fdr <= 1) * 100, 2)) %>%
  kable()

writeLines('Percent of modules whose PC1 is significantly associated')
Dx.gender %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::summarise(nsig = round(sum(pc1.fdr <= 0.05)/sum(pc1.fdr <= 1) * 100, 2)) %>%
  kable()
```

### Enrichment for differential expression
```{r Dx.enrich}
# Get differential expression gene list from synapse
load(synGet('syn10496554')@filePath)
all.used.ids = c(all.used.ids, 'syn10496554')
names(amp.ad.de.geneSets) = gsub('CER','CBE', names(amp.ad.de.geneSets))

@@

  enrichResults = plyr::ldply(modMembers, .fun = function(y, deGenes, backgroundGenes){
    plyr::ldply(deGenes, .fun = function(z, y, backgroundGenes){
      fisherEnrichment(y,z,backgroundGenes)
    }, y, backgroundGenes, .id = 'Dx.GeneSet')
  }, deGenes, backgroundGenes, .id = 'ModuleNameFull') %>%
    dplyr::mutate(fdr = p.adjust(pval))
}, .id = 'brainRegion')
```
### Enrichment for gene sets
```{r pathway.enrich}
# Download all related genesets from synapse
load(synGet('syn4867851')@filePath)
all.used.ids = c(all.used.ids, 'syn4867851')

@@

### Find overlap between modules in different brainregion
```{r module.overlap}

```

### Intereating modules
```{r int.modules}

```

### Store results in synapse
```{r syn.store, include=FALSE, eval = F}
write.table(Dx, file = 'AssociaitonStatWithDx.tsv', sep = '\t', quote = F, row.names = F)
OBJ = File('AssociaitonStatWithDx.tsv', name = 'Association with Dx', parentId = 'syn11140497')
OBJ = synStore(OBJ, used = all.used.ids, executed = thisFile, activityName = activityName)

@@

write.table(Pathway.enrich, file = 'PathwayEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ2 = File('PathwayEnrichment.tsv', name = 'Pathway Enrichment', parentId = 'syn11140497')
OBJ2 = synStore(OBJ2, used = all.used.ids, executed = thisFile, activityName = activityName)

save(list = c('assoc.stat.diagnosis', 'assoc.stat.diagnosis.gender'), file = 'AllAssociationResults.RData')
OBJ3 = File('AllAssociationResults.RData', name = 'All Assocition Statistics (RData)', parentId = 'syn11140497')
OBJ3 = synStore(OBJ3, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.enrich, file = 'DiagnosisEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ4 = File('DiagnosisEnrichment.tsv', name = 'Diagnosis Enrichment', parentId = 'syn11140497')
OBJ4 = synStore(OBJ4, used = all.used.ids, executed = thisFile, activityName = activityName)
```

>>>>

    Heatmap(mdl.ovrlp, col = colorRamp2(seq(0,1,length.out = 5), viridis::viridis(5)),
            name = 'JacDist', cell_fun = function(j,i,x,y,wifht,height,fill){
              grid.text(mdl.ovrlp.log[i,j] %>% format(digits = 1), x, y)
            })
}

# Pull gene sets code from Ben 
pullReferenceGeneSets <- function(url){
  #pull gene set from Enrichr
  foo <- RCurl::getURL(url)

  #split by carriage returns
  fooSplit <- strsplit(foo,"\n")

  #unlist
  fooSplit <- unlist(fooSplit)

  #split by tab
  fooSplit <- strsplit(fooSplit,"\t")

  #name them by the first element
  catNames <- lapply(fooSplit,function(x) x[1])
  names(fooSplit) <- catNames

  #drop the first two elements
  fooSplit <- lapply(fooSplit,function(x) x[-c(1,2)])

  fxn1 <- function(x){
    library(dplyr)
    strsplit(x,',') %>%
      sapply(function(y) y[1]) %>%
      return
  }
  #remove 1.0 from elements
  fooSplit2 <- lapply(fooSplit,fxn1)
  names(fooSplit2) <- names(fooSplit)
  return(fooSplit2)
}

pullADgenes <- function(){
  genesets1 <- synapseClient::synGet('syn5923958')
  load(synapseClient::getFileLocation(genesets1))
  dbgap <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=dbGaP")
  #kegg, wikipathways, biocarta, panther, jensen_diseases, omim_disease, omim_expanded
  kegg <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=KEGG_2016")
  wikipathways <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=WikiPathways_2016")
  jensen_diseases <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=Jensen_DISEASES")
  biocarta <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=BioCarta_2016")
  panther <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=Panther_2016")
  omim_disease <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=OMIM_Disease")
  omim_expanded <- pullReferenceGeneSets("http://amp.pharm.mssm.edu/Enrichr/geneSetLibrary?mode=text&libraryName=OMIM_Expanded")

  adList <- GeneSets$Alzheimers$`AD:GeneticLoci`
  adList <- c(adList,'HLA-DRB5','HLA-DRB1')
  adList <- adList[-which(adList=='HLA-DRB5-DRB1')]
  adList <- list(igap = adList)
  adList$dbgap <- dbgap$`Alzheimer Disease`
  adList$kegg <- kegg$`Alzheimer's disease_Homo sapiens_hsa05010`
  adList$wikipathwaysMouse <- wikipathways$`Alzheimers Disease_Mus musculus_WP2075`
  adList$wikipathwaysHuman <- wikipathways$`Alzheimers Disease_Homo sapiens_WP2059`
  adList$jensenDisease <- jensen_diseases$`Alzheimer's_disease`
  adList$biocarta <- biocarta$`Deregulation of CDK5 in Alzheimers Disease_Homo sapiens_h_p35alzheimersPathway`
  adList$pantherAmyloid <- panther$`Alzheimer disease-amyloid secretase pathway_Homo sapiens_P00003`
  adList$pantherPresenilin <- panther$`Alzheimer disease-presenilin pathway_Homo sapiens_P00004`
  adList$omim <- omim_disease$`alzheimer_disease`
  adList$omimExpanded <- omim_expanded$`alzheimer_disease`

  genecardsObj <- synapseClient::synGet('syn10507702')
  genecards <- data.table::fread(synapseClient::getFileLocation(genecardsObj),data.table=F)

  adList$genecards <- genecards$`Gene Symbol`
  return(adList)
}
```

## Association test
### Associaiton with Diagnosis
```{r Dx, fig.height=5, fig.width=10}
# Find assocition b/w Diagnosis category with n eigen genes
FORMULA = as.formula('PC~Diagnosis+Batch+RIN+PCT_INTRONIC_BASES+PMI+PCT_INTERGENIC_BASES+AOD+PCT_PF_READS_ALIGNED+Gender')
assoc.stat.diagnosis = MODULES %>%
  dplyr::filter(GeneID %in% rownames(EXPR)) %>%
  plyr::dlply(.(ModuleName, brainRegion), .fun = findAssociationStatistics, 
              COVARIATES, EXPR, FORMULA,
              .parallel = T, .paropts = list(.packages = c('dplyr', 'data.table')))

@@

writeLines('Percent of modules whose PC1 is significantly associated')
Dx %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::summarise(nsig = round(sum(pc1.fdr <= 0.05)/sum(pc1.fdr <= 1) * 100, 2)) %>%
  kable()
```
### Associaiton with Diagnosis.Gender
```{r Dx.Gender, fig.height=5, fig.width=10}
# Find assocition b/w Diagnosis.Gender category with n eigen genes
COVARIATES$Diagnosis.Gender = paste(COVARIATES$Diagnosis, COVARIATES$Gender, sep= '.') %>%
  as.factor
FORMULA = as.formula('PC~Diagnosis.Gender+Batch+RIN+PCT_INTRONIC_BASES+PMI+PCT_INTERGENIC_BASES+AOD+PCT_PF_READS_ALIGNED')
assoc.stat.diagnosis.gender = MODULES %>%
  dplyr::filter(GeneID %in% rownames(EXPR)) %>%
  plyr::dlply(.(ModuleName, brainRegion), .fun = findAssociationStatistics, 
              COVARIATES, EXPR, FORMULA,
              .parallel = T, .paropts = list(.packages = c('dplyr', 'data.table')))

@@

@@

writeLines('Significantly associated modules')
Dx.gender %>%
  dplyr::filter(total.fdr <= 0.05) %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::arrange(desc(total.eff.sz)) %>%
  kable()
```
Comparison b/w Dx and Dx.gender
```{r Dx.Gender.1, fig.height=5, fig.width=10}
tmp = dplyr::left_join(Dx %>%
                         dplyr::select(ModuleName, brainRegion, total.eff.sz, total.fdr) %>%
                         dplyr::rename(Dx = total.eff.sz, Dx.fdr = total.fdr),
                       Dx.gender %>%
                         dplyr::select(ModuleName, brainRegion, total.eff.sz, total.fdr) %>%
                         dplyr::rename(Dx.gender = total.eff.sz, Dx.gender.fdr = total.fdr))
p = ggplot(tmp, aes(x = Dx, y = Dx.gender, color = -log10(Dx.fdr+1e-100))) + geom_point() + facet_grid(.~brainRegion) + geom_smooth(method = 'lm')
p = p +scale_color_continuous(low = 'white', high = 'red')
p
```
### Association with Diagnosis in female samples
```{r Dx.female, fig.height=5, fig.width=10}
# Find assocition b/w Diagnosis category with n eigen genes in female samples
FORMULA = as.formula('PC~Diagnosis+Batch+RIN+PCT_INTRONIC_BASES+PMI+PCT_INTERGENIC_BASES+AOD+PCT_PF_READS_ALIGNED')
ind = COVARIATES$SampleID[COVARIATES$Gender == 'FEMALE']
assoc.stat.diagnosis.female = MODULES %>%
  dplyr::filter(GeneID %in% rownames(EXPR)) %>%
  plyr::dlply(.(ModuleName, brainRegion), .fun = findAssociationStatistics, 
              COVARIATES[COVARIATES$SampleID %in% ind,], EXPR[,ind], FORMULA,
              .parallel = T, .paropts = list(.packages = c('dplyr', 'data.table')))

Dx.female = lapply(assoc.stat.diagnosis.female, function(x) x$assoc.stat) %>%
  data.table::rbindlist(use.names = T, fill = T, idcol = 'ModuleName.BrainRegion') %>%
  tidyr::separate(ModuleName.BrainRegion, c('ModuleName', 'brainRegion'), sep = '\\.') %>%
  dplyr::left_join(MODULES %>%
                     dplyr::select(Module, method, ModuleName, brainRegion, ModuleNameFull) %>%
                     unique()) %>%
  plyr::ddply(.(brainRegion), .fun = function(x){
    x %>%
      dplyr::mutate(total.fdr = p.adjust(total.pval))
  }) %>%
  dplyr::mutate(total.sig = total.fdr <= 0.05)

p = ggplot(Dx.female, aes(x = brainRegion, y = total.eff.sz)) + geom_boxplot() + geom_jitter(aes(color = total.sig))
p = p + coord_flip() + xlab('Brain Region') + ylab('Total Effect Size')
# p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')

writeLines('Significantly associated modules')
Dx.female %>%
  dplyr::filter(total.fdr <= 0.05) %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::arrange(desc(total.eff.sz)) %>%
  kable()
```
### Association with Diagnosis in male samples
```{r Dx.male, fig.height=5, fig.width=10}
# Find assocition b/w Diagnosis category with n eigen genes in female samples
FORMULA = as.formula('PC~Diagnosis+Batch+RIN+PCT_INTRONIC_BASES+PMI+PCT_INTERGENIC_BASES+AOD+PCT_PF_READS_ALIGNED')
ind = COVARIATES$SampleID[COVARIATES$Gender == 'MALE']
assoc.stat.diagnosis.male = MODULES %>%
  dplyr::filter(GeneID %in% rownames(EXPR)) %>%
  plyr::dlply(.(ModuleName, brainRegion), .fun = findAssociationStatistics, 
              COVARIATES[COVARIATES$SampleID %in% ind,], EXPR[,ind], FORMULA,
              .parallel = T, .paropts = list(.packages = c('dplyr', 'data.table')))

Dx.male = lapply(assoc.stat.diagnosis.female, function(x) x$assoc.stat) %>%
  data.table::rbindlist(use.names = T, fill = T, idcol = 'ModuleName.BrainRegion') %>%
  tidyr::separate(ModuleName.BrainRegion, c('ModuleName', 'brainRegion'), sep = '\\.') %>%
  dplyr::left_join(MODULES %>%
                     dplyr::select(Module, method, ModuleName, brainRegion, ModuleNameFull) %>%
                     unique()) %>%
  plyr::ddply(.(brainRegion), .fun = function(x){
    x %>%
      dplyr::mutate(total.fdr = p.adjust(total.pval))
  }) %>%
  dplyr::mutate(total.sig = total.fdr <= 0.05)

p = ggplot(Dx.male, aes(x = brainRegion, y = total.eff.sz)) + geom_boxplot() + geom_jitter(aes(color = total.sig))
p = p + coord_flip() + xlab('Brain Region') + ylab('Total Effect Size')
# p = p + scale_color_continuous(low = 'white', high = 'red')
p + theme(legend.position = 'top')

writeLines('Significantly associated modules')
Dx.male %>%
  dplyr::filter(total.fdr <= 0.05) %>%
  dplyr::group_by(brainRegion) %>%
  dplyr::arrange(desc(total.eff.sz)) %>%
  kable()
```

## Enrichment analysis
### Enrichment for differential expression
```{r Dx.enrich, fig.height=10, fig.width=12}
# Get differential expression gene list from synapse
load(synGet('syn10496554')@filePath)
all.used.ids = c(all.used.ids, 'syn10496554')
names(amp.ad.de.geneSets) = gsub('CER','CBE', names(amp.ad.de.geneSets))

@@

  enrichResults = plyr::ldply(modMembers, .fun = function(y, deGenes, backgroundGenes){
    plyr::ldply(deGenes, .fun = function(z, y, backgroundGenes){
      fisherEnrichment(y,z,backgroundGenes)
    }, y, backgroundGenes, .id = 'Dx.GeneSet')
  }, deGenes, backgroundGenes, .id = 'ModuleNameFull') %>%
    dplyr::mutate(fdr = p.adjust(pval))
}, .id = 'brainRegion')

writeLines('Comparison b/w Dx and Dx.gender')
Dx.enrich1 = Dx.enrich %>%
  dplyr::select(-Genes) %>%
  tidyr::separate(Dx.GeneSet, c('brainRegion', 'Comparison', 'Gender', 'Direction'), sep = '\\.')
Dx.enrich1$Direction[is.na(Dx.enrich1$Direction)] = Dx.enrich1$Gender[is.na(Dx.enrich1$Direction)]
Dx.enrich1$Gender = gsub('UP', 'ALL', Dx.enrich1$Gender)
Dx.enrich1$Gender = gsub('DOWN', 'ALL', Dx.enrich1$Gender)
Dx.enrich1 = dplyr::filter(Dx.enrich1, Comparison == 'AD-CONTROL', fdr <= 0.05)
p = ggplot(Dx.enrich1, aes(x = Gender, y = -log10(fdr))) + geom_boxplot() 
p = p + coord_flip() + facet_grid(.~brainRegion, scales = 'free') + geom_jitter(aes(color = Direction))
pl = list();pl[[1]] = p + ylab('') + theme(legend.position = 'top')

p = ggplot(Dx.enrich1, aes(x = Gender, y = Odds.Ratio)) + geom_boxplot() 
p = p + coord_flip() + facet_grid(.~brainRegion, scales = 'free') + geom_jitter(aes(color = Direction))
pl[[2]] = p + ylab('') + theme(legend.position = 'top')
multiplot(plotlist = pl, cols = 1)
```

### Enrichment for AD related gene sets
```{r AD.enrich, results='asis'}
# Get all AD related genesets
GeneSets = pullADgenes()

backgroundGenes = unique(MODULES$external_gene_name)
geneSet.ref = list(AD = GeneSets) %>%
  CovariateAnalysis::filterGeneSets(backgroundGenes)
geneSet.ref = geneSet.ref$AD

# Perform enrichment analysis
AD.enrich = plyr::ddply(MODULES, .(ModuleNameFull), .fun = function(mod, geneSetRef, backgroundGenes){
  modMembers = unique(mod$external_gene_name)

  enrichResults = plyr::ldply(geneSetRef, .fun = function(y, modMembers, backgroundGenes){
    fisherEnrichment(y, modMembers, backgroundGenes)
  }, modMembers, backgroundGenes, .id = 'GeneSetName', .parallel = T, 
  .paropts = list(.packages = c('CovariateAnalysis'))) %>%
    dplyr::mutate(fdr = p.adjust(pval))
}, 
.id = 'ModuleNameFull', geneSet.ref, backgroundGenes)

writeLines('AD related pathways enriched an fdr of 0.05')
AD.enrich %>%
  dplyr::select(ModuleNameFull, GeneSetName, Odds.Ratio, fdr) %>%
  dplyr::filter(fdr <= 0.05) %>%
  dplyr::left_join(MODULES %>%
                     dplyr::select(ModuleNameFull, brainRegion)) %>%
  unique() %>%
  dplyr::arrange(desc(brainRegion), desc(Odds.Ratio)) %>%
  kable()
```

### Enrichment for other gene sets
```{r pathway.enrich, results='asis'}
# Get all enrichr genesets
load(synGet('syn4867851')@filePath)
all.used.ids = c(all.used.ids, 'syn4867851')

@@

## Module Selection
### Interesting modules for diagnosis
```{r int.modules.1, fig.height=7, fig.width=7, results='asis'}
# Wrt case control
Dx.modules = dplyr::inner_join(Dx %>% 
                                 dplyr::filter(total.fdr <= 0.05) %>%
                                 dplyr::select(ModuleNameFull, brainRegion, total.eff.sz, total.fdr) %>%
                                 dplyr::rename(assoc.eff.sz = total.eff.sz, assoc.fdr = total.fdr),
                               Dx.enrich1 %>%
                                 dplyr::filter(fdr <= 0.05, Gender == 'ALL') %>%
                                 dplyr::select(ModuleNameFull, brainRegion, Direction, Odds.Ratio, fdr) %>%
                                 dplyr::rename(diffexp.fdr = fdr, diffexp.or = Odds.Ratio)) %>%
  dplyr::left_join(AD.enrich %>%
                     dplyr::filter(fdr <= 0.05) %>%
                     dplyr::select(ModuleNameFull, GeneSetName, Odds.Ratio, fdr) %>%
                     dplyr::rename(ad.fdr = fdr, ad.or = Odds.Ratio)) %>%
  dplyr::arrange((brainRegion), (Direction), desc(assoc.eff.sz))
writeLines('Imporatant Modules for case control comparison')
kable(Dx.modules)
```

### Interesting modules for diagnosis.gender
```{r int.modules.2, fig.height=7, fig.width=7, results='asis'}
# Wrt gender specific case control
Dx.gender.modules = dplyr::inner_join(Dx.gender %>% 
                                        dplyr::filter(total.fdr <= 0.05) %>%
                                        dplyr::select(ModuleNameFull, brainRegion, total.eff.sz, total.fdr) %>%
                                        dplyr::rename(assoc.eff.sz = total.eff.sz, assoc.fdr = total.fdr),
                                      Dx.enrich1 %>%
                                        dplyr::filter(fdr <= 0.05, Gender %in% c('MALE', 'FEMALE')) %>%
                                        dplyr::select(ModuleNameFull, brainRegion, Direction, Odds.Ratio, fdr) %>%
                                        dplyr::rename(diffexp.fdr = fdr, diffexp.or = Odds.Ratio)) %>%
  dplyr::left_join(AD.enrich %>%
                     dplyr::filter(fdr <= 0.05) %>%
                     dplyr::select(ModuleNameFull, GeneSetName, Odds.Ratio, fdr) %>%
                     dplyr::rename(ad.fdr = fdr, ad.or = Odds.Ratio)) %>%
  dplyr::arrange((brainRegion), (Direction), desc(assoc.eff.sz))
writeLines('Imporatant Modules for gender specific case control comparison')
kable(Dx.gender.modules)

# Wrt case control in females
Dx.female.modules = dplyr::inner_join(Dx.female %>% 
                                        dplyr::filter(total.fdr <= 0.05) %>%
                                        dplyr::select(ModuleNameFull, brainRegion, total.eff.sz, total.fdr) %>%
                                        dplyr::rename(assoc.eff.sz = total.eff.sz, assoc.fdr = total.fdr),
                                      Dx.enrich1 %>%
                                        dplyr::filter(fdr <= 0.05, Gender %in% c('FEMALE')) %>%
                                        dplyr::select(ModuleNameFull, brainRegion, Direction, Odds.Ratio, fdr) %>%
                                        dplyr::rename(diffexp.fdr = fdr, diffexp.or = Odds.Ratio)) %>%
  dplyr::left_join(AD.enrich %>%
                     dplyr::filter(fdr <= 0.05) %>%
                     dplyr::select(ModuleNameFull, GeneSetName, Odds.Ratio, fdr) %>%
                     dplyr::rename(ad.fdr = fdr, ad.or = Odds.Ratio)) %>%
  dplyr::arrange((brainRegion), (Direction), desc(assoc.eff.sz))
writeLines('Imporatant Modules for case control comparison in females')
kable(Dx.female.modules)

# Wrt case control in males
Dx.male.modules = dplyr::inner_join(Dx.male %>% 
                                      dplyr::filter(total.fdr <= 0.05) %>%
                                      dplyr::select(ModuleNameFull, brainRegion, total.eff.sz, total.fdr) %>%
                                      dplyr::rename(assoc.eff.sz = total.eff.sz, assoc.fdr = total.fdr),
                                    Dx.enrich1 %>%
                                      dplyr::filter(fdr <= 0.05, Gender %in% c('MALE')) %>%
                                      dplyr::select(ModuleNameFull, brainRegion, Direction, Odds.Ratio, fdr) %>%
                                      dplyr::rename(diffexp.fdr = fdr, diffexp.or = Odds.Ratio)) %>%
  dplyr::left_join(AD.enrich %>%
                     dplyr::filter(fdr <= 0.05) %>%
                     dplyr::select(ModuleNameFull, GeneSetName, Odds.Ratio, fdr) %>%
                     dplyr::rename(ad.fdr = fdr, ad.or = Odds.Ratio)) %>%
  dplyr::arrange((brainRegion), (Direction), desc(assoc.eff.sz))
writeLines('Imporatant Modules for case control comparison in males')
kable(Dx.male.modules)
```
### Find overlap between modules in different brainregion
```{r module.overlap, fig.height=5, fig.width=10, eval = F}
# FisherEnrichment b/w modules
MOD.MEMBERS = plyr::dlply(MODULES, .(ModuleNameFull), .fun = function(x) unique(x$external_gene_name))
MOD.OVRLP = plyr::ldply(MOD.MEMBERS, .fun = function(x, modMembers, backgroundGenes){
  plyr::ldply(modMembers, .fun = function(y, x, backgroundGenes){
    fisherEnrichment(y, x, backgroundGenes)
  }, x, backgroundGenes, .parallel = T, .paropts = list(.packages = c('CovariateAnalysis')), .id = 'MOD1') %>%
    dplyr::rename(MOD1 = ModuleNameFull)
}, MOD.MEMBERS, backgroundGenes, .id = 'MOD2') %>%
  dplyr::select(-Genes) %>%
  dplyr::rename(MOD2 = ModuleNameFull)
```

### Store results in synapse
```{r syn.store, include=FALSE, eval = F, cache=FALSE}
write.table(Dx, file = 'AssociaitonStatWithDx.tsv', sep = '\t', quote = F, row.names = F)
OBJ = File('AssociaitonStatWithDx.tsv', name = 'Association with Dx', parentId = 'syn11140497')
OBJ = synStore(OBJ, used = all.used.ids, executed = thisFile, activityName = activityName)

@@

write.table(Dx.feamle, file = 'AssociaitonStatWithDxFemale.tsv', sep = '\t', quote = F, row.names = F)
OBJ2 = File('AssociaitonStatWithDxFemale.tsv', name = 'Association with Dx.Female', parentId = 'syn11140497')
OBJ2 = synStore(OBJ2, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.male, file = 'AssociaitonStatWithDxMale.tsv', sep = '\t', quote = F, row.names = F)
OBJ3 = File('AssociaitonStatWithDxMale.tsv', name = 'Association with Dx.Male', parentId = 'syn11140497')
OBJ3 = synStore(OBJ3, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Dx.enrich, file = 'DiffEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ4 = File('DiffEnrichment.tsv', name = 'Differential Expression Enrichment', parentId = 'syn11140497')
OBJ4 = synStore(OBJ4, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(AD.enrich, file = 'ADEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ5 = File('ADEnrichment.tsv', name = 'AD Enrichment', parentId = 'syn11140497')
OBJ5 = synStore(OBJ5, used = all.used.ids, executed = thisFile, activityName = activityName)

write.table(Pathway.enrich, file = 'PathwayEnrichment.tsv', sep = '\t', quote = F, row.names = F)
OBJ6 = File('PathwayEnrichment.tsv', name = 'Pathway Enrichment', parentId = 'syn11140497')
OBJ6 = synStore(OBJ6, used = all.used.ids, executed = thisFile, activityName = activityName)

save(list = c('assoc.stat.diagnosis', 'assoc.stat.diagnosis.gender', 
              'assoc.stat.diagnosis.female', 'assoc.stat.diagnosis.male'), 
     file = 'AllAssociationResults.RData')
OBJ7 = File('AllAssociationResults.RData', name = 'All Assocition Statistics (RData)', parentId = 'syn11140497')
OBJ7 = synStore(OBJ7, used = all.used.ids, executed = thisFile, activityName = activityName)
```
